### 2015-05-04 writing/SNLI paper/newcorpus.tex
Paper update

\section{Discussion and conclusion}\label{sec:discussion}

@@

aim to surpass sick in both size and label consistency

>>>>

\section{A new corpus for natural language inference}\label{sec:discussion}

need for new corpus

Our ultimate aim in this work is to develop supervised models for sentence representation that can accurately capture natural language meaning. While sentiment tasks like SST have provided a useful testbed for sentence representation models, sentiment labeling only requires that models be able to encode a small piece of the full expressive capacity of language. We claim that the task of natural language inference (also called recognizing textual entailment, or RTE) is significantly more demanding, and that strong performance on this task is good evidence of a model's overall strength in sentence representation.

what's new
- size
- grounding

@@

aim to surpass sick in both size and r consistency

Since our goal is to evaluate the quality of the single sentence representations in our model, we train an entailment classifier that has access only to the output of our sentence representation model, and not to any of the word or phrase representations that it used. We encourage future users of this corpus to evaluate their models in this way when possible. Our classifier is simply a stack of three 100d (NONLIN) layers, with the bottom layer taking the concatenated sentence representations as input and the top layer feeding a softmax classifier, all trained jointly with the representation model itself.
